---
title: "Assignment 3 - Mapping"
author: "EmilyStarer"
format: html
editor: visual
---

## Summary

The data source is advertising media data. The data is from actual advertising campaigns. I chose to highlight the number of Advertisers per state with live media. The goal of this map is to understand a ranking of media by state to better understand how to focus efforts geographically. I decided to count the distinct number of advertisers per state and merge that with the original dataset. The spacial units are state using ggplot to great the state.

## Import Data Source

Import of the library. Using `echo: false` option to disable the printing of code (only output is displayed).

```{r}
#| echo: false
library(tidyverse)
library(plotly)
library(maps)
library(ggplot2)
library(ggdendro)
library(plotly)
library(usmap)
```

Import of the data source

```{r}
#read in data
library(readr)
geo <- read.csv("geomediadata1.csv") ## Since this is a technical issue, I decided to help her knit the file. -- Kevin
#add in geometry column to data fame
us_geo_data <- map_data("state") %>%mutate(Region.Name=str_to_title(region))

us_geo_data <- left_join(us_geo_data,geo,
          by="Region.Name", all=T)
```

```{r}
### us co-ordinate
new_us_geo_data <- us_geo_data %>%
  dplyr::select(region, long, lat) %>%
  unique()

#count of advertisers per state 
Adv <- us_geo_data %>% group_by(region) %>%
  summarize (distinct_adv = n_distinct(Advertiser.Name))

#add in count of advertiser name 
new_geo_grouped <- right_join(new_us_geo_data, Adv, by="region", all=T)
```

```{r}
new_plot <- ggplot(new_geo_grouped, 
       mapping = aes(x = long, y = lat, group = region, 
                     fill = distinct_adv,
                     text = paste("Number of Advertisers:", round(distinct_adv)))) +
  geom_polygon(color="white") +
  ggdendro::theme_dendro() +
  guides(fill=guide_legend(title="Number of Advertisers per State serving Media")) +
  coord_map() + 
  ggtitle("Number of Advertisers per State serving Media")

ggplotly(new_plot, tooltip = "text")
```
